Abstract

### 2013-09-26 Abstract.tex
Updated and compiled Abstract + ES

\documentclass[12pt, Arial]{article}
\title{Executive Summary}
\author{How to Teach a Class to Grade Itself Using Game Theory}
\begin{document}
\maketitle
This research project focuses on the development of a novel and efficient peer grading system for online courses by Coursera or EDx. In such courses, the amount of students can be enormous. To grade the number of assignments produced, multiple choice tests and automated grading systems have been employed, but these run into limitations when grading open-ended responses such as essays. The underlying complexity of peer grading arises from the nature of human behavior. Our approach to this problem utilizes game theory and mechanism design --- a first of its kind to our knowledge. Our research proposes three mechanisms, each with more realism than the previous. To compare mechanisms, we defined a benchmark based on the accuracy of grades and workload of student and professor. Using this benchmark, the final mechanism we created surpasses both traditional peer grading and automated grading methods.  Our work facilitates and standardizes future work for peer grading and mechanism development, ultimately improving the quality of online education.
\end{document}

>>>>

\documentclass[12pt, Arial]{article}
\title{Abstract}
\author{How to Teach a Class to Grade Itself Using Game Theory}
\date{}
\begin{document}
\maketitle
An efficient peer grading mechanism is proposed for grading the multitude of assignments in online courses. This novel approach is based on game theory and mechanism design. A set of assumptions and a mathematical model is ratified to simulate the dominant strategy behavior of students in a given mechanism. A benchmark function accounting for grade accuracy and workload is established to quantitatively compare effectiveness and scalability of various mechanisms. After iteration of mechanisms under increasingly realistic assumptions, three are proposed: Calibration, Improved Calibration and Deduction. The Deduction mechanism performs relatively well in the benchmark, outperforming traditional automated and peer grading systems. The mathematical model and benchmark opens the way for future derivative works to be performed and compared.
\end{document}
